Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-02 papers/BON_VHDL/paper.tex
sistematisation

\documentclass{article} 
\usepackage{times}

\usepackage{ifpdf}
\usepackage{a4wide}
\usepackage{pdfsync}

@@

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\Sc}{\emph{system\_chart}\xspace}
\newcommand{\Clc}{\emph{cluster\_chart}\xspace}
\newcommand{\Csc}{\emph{class\_chart}\xspace}
\newcommand{\Ft}{\emph{feature}\xspace}
\newcommand{\ent}{\emph{entity}\xspace}
\newcommand{\arch}{\emph{architecture}\xspace}
\newcommand{\archs}{\emph{architectures}\xspace}
\newcommand{\duc}{\emph{design units collection}\xspace}
\newcommand{\ducs}{\emph{design units collections}\xspace}
\newcommand{\du}{\emph{design unit}\xspace}
%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design and refinement calculus, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.  
\section{Refinement from BON to VHDL-AMS}

\subsection{Mapping between BON and VHDL-AMS}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\begin{itemize}
\item \Sc: VHDL-AMS allows hierarchical structure modeling, 
meaning that subsistems ( \ducs ), can be developed independently.
As an top-level description (informal/formal), \Sc connect all the \ducs
together to a complete design. 
\item \Clc: An  subsistem which represent \duc.
\item \Csc: describes \du. It can be identify with the primary unit (\ent) and secondary 
unit (\arch) structure in VHDL-AMS.
The \Csc's name corresponds to the name of the entity in VHDL-AMS.
\item \Ft: The feature section of the \Csc, where the mathematical 
transfer function of the component is entered, holds the same information 
as the \arch section of the VHDL-AMS.
\end{itemize}
An VHDL-AMS component are described using an \ent-\arch structure. 
The component model contains an \ent and one or more \archs. 
The \ent specifies the interface of the model to the outside world. 
In other words, \ent introduces a name, list of input/output ports 
and the definition of the generic parameters. The textual 
presentation of \ent is shown in Figure.1. 
\input{adc-entity}

>>>>

\documentclass{article} 
\usepackage{times}
\usepackage{multirow}
\usepackage{ifpdf}
\usepackage{a4wide}
\usepackage{pdfsync}

@@

\newcommand{\tablesize}{\footnotesize}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\myhref}[2]{\ifpdf\href{#1}{#2}\else\htmladdnormallinkfoot{#2}{#1}\fi}
%\newcommand{\myhref}[2]{\emph{#2}}
\newcommand{\todo}{\textbf{TODO:}}
\newcommand{\ST}{\emph{SenseTile}\xspace}
\newcommand{\STs}{\emph{SenseTiles}\xspace}
\newcommand{\STS}{\emph{SenseTile Simulator}\xspace}
\newcommand{\datastore}{\STs Scientific Datastore\xspace}
\newcommand{\computefarm}{The \STs Scientific Compute Farm\xspace}
\newcommand{\computefarmlong}{UCD CASL \STs Software and Data Compute Server Farm\xspace}
\newcommand{\sensorfarm}{The \STs\xspace}
\newcommand{\Sc}{\emph{SYSTEM\_CHART}\xspace}
\newcommand{\Clc}{\emph{CLUSTER\_CHART}\xspace}
\newcommand{\Csc}{\emph{CLASS\_CHART}\xspace}
\newcommand{\Ft}{\emph{feature}\xspace}
\newcommand{\ent}{\emph{entity}\xspace}
\newcommand{\arch}{\emph{architecture}\xspace}
\newcommand{\archs}{\emph{architectures}\xspace}
\newcommand{\duc}{\emph{design units collection}\xspace}
\newcommand{\ducs}{\emph{design units collections}\xspace}
\newcommand{\du}{\emph{design unit}\xspace}
\newcommand{\undef}{\emph{undefined}\xspace}
%---------------------------------------------------------------------
% New commands, macros, \etc
%---------------------------------------------------------------------

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design and refinement calculus, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.  
\section{Mapping between BON and VHDL-AMS}
\subsection{Static model mapping}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\begin{center}
    \begin{tabular}{|l|l|l|}
    	\hline
    	VHDL-AMS & BON & Description \\ \hline
    	\ducs (packages) & \Sc & 
	\begin{minipage}[c]{7cm} 
                 \vskip 3mm
    		VHDL-AMS allows hierarchical structure modeling, 
    		meaning that subsistems (\ducs), can be developed independently.
    		As an top-level description (informal/formal), \Sc connect all the \ducs
    		together to a complete design. Actually \Sc can be understood 
                as VHDL-AMS package as a way of grouping a collection of related 
                declarations that serve a common purpose.
                \\ 
    	\end{minipage}\\ \hline
        \duc & \Clc &
	\begin{minipage}[c]{7cm} 
                \vskip 3mm
		An  subsistem which represent \duc.
                \\ 
    	\end{minipage}\\ \hline
	 \du & \Csc &
	\begin{minipage}[c]{7cm}
	      \vskip 3mm	 
              \Csc  describes \du. It can be identify with the primary unit (\ent) and secondary 
	      unit (\arch) structure in VHDL-AMS.
	      The \Csc's name corresponds to the name of the entity in VHDL-AMS.
              \\
    	\end{minipage}\\ \hline
        \arch & \Ft & 
	\begin{minipage}[c]{7cm} 
              \vskip 3mm
	      The feature section of the \Csc, where the mathematical 
	      transfer function of the component is entered, holds the same information 
	      as the \arch section of the VHDL-AMS.
              \\
    	\end{minipage}\\ \hline

    \end{tabular}
\end{center}
\subsection{Operators-expressions mapping}
%\todo{dragan 27/07/2009 - Figure out :  VHDL-ASM as BON  represents an strongly typed language.}
This subsection summarises all relations on expressions - operators between VHDL-AMS and BON.
\begin{center}
    \begin{tabular}{|c|c|l|}
    	\hline
    	VHDL-AMS & BON & Description \\ \hline
    	\begin{minipage}[c]{2cm} 
         \centering 
         \textbf{**}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \textbf{\textasciicircum}
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		exponentiation.
                \\ 
    	\end{minipage}\\ \hline

       \begin{minipage}[c]{2cm} 
         \centering 
         \textbf{+, \textendash, *, /}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \textbf{+, \textendash, *, /}
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		identity, addition, negation, subtraction, multiplication, division.
                \\ 
    	\end{minipage}\\ \hline

       \begin{minipage}[c]{2cm} 
         \centering 
         \textbf{=, /=, \textless, \textless=, \textgreater, \textgreater=, mod}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \textbf{=, /=, \textless, \textless=, \textgreater, \textgreater=, $\backslash\backslash$}
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		equality, inequality, less than, less than or equal , greater than, greater than or equal, modulo.
                \\ 
    	\end{minipage}\\ \hline

       \begin{minipage}[c]{2cm} 
         \centering 
         \textbf{not, and, or, xor}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \textbf{not, and, or, xor}
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		 	negation, logical and, logical or, exclusive or.
                \\ 
    	\end{minipage}\\ \hline

	\begin{minipage}[c]{2cm} 
         \centering 
         \textbf{nand}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \textbf{not and}
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		 	negated logical and.
                \\ 
    	\end{minipage}\\ \hline

        \begin{minipage}[c]{2cm} 
         \centering 
         \textbf{nor}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \textbf{not or}
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		 	negated logical or.
                \\ 
    	\end{minipage}\\ \hline

	 \begin{minipage}[c]{2cm} 
         \centering 
         \textbf{xnor}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \textbf{not xor}
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		 	negated exclusive or.
                \\ 
    	\end{minipage}\\ \hline

	\begin{minipage}[c]{2cm} 
         \centering 
         \textbf{sll, srl, sla, sra, rol, ror}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \undef
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		 	shift-left/right logical,\\
                        shift-left/right arithmetic,\\
                        rotate left/right.
                \\ 
    	\end{minipage}\\ \hline

       \begin{minipage}[c]{2cm} 
         \centering 
         \textbf{rem}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \undef
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		 	reminder.
                \\ 
    	\end{minipage}\\ \hline

       \begin{minipage}[c]{2cm} 
         \centering 
         \textbf{abs}
        \end{minipage}  
        &
       \begin{minipage}[c]{2cm}
         \centering 
         \undef
        \end{minipage}  
        & 
	\begin{minipage}[c]{5cm} 
                 \vskip 3mm
    		 	absolute value.
                \\ 
    	\end{minipage}\\ \hline

    \end{tabular}
\end{center}
\subsection{Type mapping}

\section{Refinement from BON to VHDL-AMS}

An VHDL-AMS component are described using an \ent-\arch structure. 
The component model contains an \ent and one or more \archs. 
The \ent specifies the interface of the model to the outside world. 
In other words, \ent introduces a name, list of input/output ports 
and the definition of the generic parameters. The textual 
presentation of \ent is shown in Figure.1. 
\input{adc-entity}
